---
title: "Bootstrap Confidence Intervals"
subtitle: "Part II"
author: ""
date: ""
output: 
  html_document:
    toc: false
    number_sections: false
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Packages and Data

```{r packages}
library(tidyverse)
library(infer)
```

The data is from https://archive.ics.uci.edu/ml/datasets/Liver+Disorders.

Each observation in the dataset constitutes the record of a male 
individual. The first 5 variables are all blood tests which are thought to be 
sensitive to liver disorders that might arise from excessive alcohol 
consumption. The last variable is meaningless, and we will drop it once we
assign variable names.

Read in the data directly from the site with `read_delim()`. Function
`str_c()` (from `stringr` in `tidyverse`) is for string concatenation and 
allows us to break up long strings. This is a nice way to keep your code 
within 80 characters.

```{r read_data}
liver <- read_delim(str_c("https://archive.ics.uci.edu/ml/",
                          "machine-learning-databases/liver-disorders/",
                          "bupa.data"), 
                    delim = ",", col_names = FALSE)
```

**Feature Information (as given in the data):**

1. `mcv` mean corpuscular volume
2. `alkphos` alkaline phosphotase
3. `sgpt` alanine aminotransferase
4. `sgot` aspartate aminotransferase
5. `gammagt` gamma-glutamyl transpeptidase
6. `drink_qty` number of half-pint equivalents of alcoholic beverages drunk per day
7. selector field created by the BUPA researchers to split the data into 
   train/test sets
   
Let's set the variable names in the tibble and drop the last variable. 

```{r parse_data}
liver <- liver %>% 
  select(mcv = X1, alkphos = X2, sgpt = X3, sgot = X4, gammagt = X5, 
         drink_qty = X6) %>% 
  mutate(drink = if_else(drink_qty > 2, "yes", "no"),
         drink = factor(drink))
```

We created a new variable, `drink`, using `mutate()`. What does it mean?

```{r preview_data}
liver
```


# Exercises

## Part 1

#### Exercise 1

Use the sample data to create a 96% confidence interval for the mean 
corpuscular volume for all males. What assumptions must you make?

#### Exercise 2

Write out an interpretation of your interval from Exercise 1.

## Part 2

Your goal will now be to create a 96% confidence interval for the mean 
difference in corpuscular volume for those males that have more than 2 drinks 
per day and those that don't. Define the difference as more than 2 drinks minus 
those with less than or equal to 2 drinks.

#### Exercise 3

Before you get started, consult 
https://infer.netlify.com/articles/flights_examples.html#one-numerical-variable-one-categorical-2-levels-diff-in-means-1

What do you need to change in `specify()` and `calculate()`?

#### Exercise 4

Plot the bootstrapped sampling distribution for the difference in
means. Comment on what you observe.

```{r echo=FALSE, eval=FALSE}
boot_dist <- liver %>% 
  specify(mcv ~ drink) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in means", order = c("yes", "no"))
```

```{r echo=FALSE, eval=FALSE}
visualise(boot_dist)
```

#### Exercise 5

Create a **96%** confidence interval for the mean 
difference in corpuscular volume for those males that have more than 2 drinks 
per day and those that don't.

```{r echo=FALSE, eval=FALSE}
boot_dist %>% 
    summarize(lb = quantile(stat, .02),
              ub = quantile(stat, .98))
```

#### Exercise 6

Write out an interpretation of your interval from Exercise 5.

# Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

# References

1. UCI Machine Learning Repository: Liver Disorders Data Set. (2020). 
   Archive.ics.uci.edu. Retrieved 9 March 2020, from 
   https://archive.ics.uci.edu/ml/datasets/Liver+Disorders
